Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-08 paper/paper.tex

\begin{figure}[t]
%  \vspace{-2ex}
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}
  }
  \caption{\label{fig:summary}Summary of bug reports.\Gustavo{Não esquecer de atualizar as figuras.
  }}
  \vspace{-3ex}
\end{figure}

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google),
\smonkey{} (Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}).
Each stacked bar breaks down the bugs
per status (\eg{}, ``1-New''). The prefix number indicates the
ordering that status labels are assigned. Several of these
reports have the label ``3-Fixed'', indicating that bug fixes have
been incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation{} bugs (of which,
\noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Most bugs we found are of moderate severity.

@@

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is empirical:
we provide a comprehensive study analyzing the effectiveness of
test transplantation and differential testing
in revealing functional bugs in popular \javascript\ engines.
Additional contributions are:
1)~A number of bugs found and fixed.
We reported a total of \totalBugsReported{} bugs.
Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed.
2)~An infrastructure for performing test transplantation and differential testing.
Both the scripts to run the experiments and the data processed are publicly available at \dataRepo{}.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:engines}Engines selected.}
  \begin{tabular}{cccrrr}
    \toprule
    Team & Name & URL & \# Stars  & DOB \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & 3300+ & Jun 2001 \\
    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008 \\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009 \\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & 1100+ & Mar 1996 \\
    Facebook & \hermes & \cite{hermes2020repo} & 5400+ & Jul 2019 \\
   \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc{} and
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
shows the number of test cases whose executions do not throw
dynamic type errors in any of the engines because of an undefined variable or property.
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc{}'s
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. For the evaluation of test transplantation, we used
the \totalTestFilesForTestTransplantation{} tests included in the
dashed rectangle under column ``type-in-all'', \ie{}, all tests under
that column but the Test262 tests. We did not consider tests from the
conformance suite as they are more likely to indicate missing features
as opposed to bugs. In addition, engine developers have access to
these test and are encouraged to run them. Finally, column
``no-fail-in-all'' shows the tests for which all engines pass. Note
that the set of tests in this column is a subset of the
``type-in-all'' test set. This test set is used in the evaluation of
differential testing as fuzzing seeds. The guarantee that they pass in
all engines assures that, if discrepancies occur, they are related to
the changes in the input as opposed to the original cause of failure.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
    shows the tests used for test transplantation (resp., cross-engine
    differential testing).\Gustavo{Terminar essa tabela}}  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc{} & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    \chakra & \cite{chakracore}\\
    \hermes & \cite{hermes2020repo}\\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    Hermes & \cite{jsi} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{}\\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
depend on external libraries, which not all selected engines
support. We decided to discard those. For example, many tests we found
required a Node.js runtime~\cite{node} for execution. Also, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.
Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc{}; we discarded those to avoid repetition and to give
credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
worth mentioning that some engines use a custom shell to run tests,
including a harness with specific assertions.  For that, we needed to
make minor changes in the testing infrastructure to be able to run the
tests uniformly across all engines. More precisely, we needed to mock
non-portable harness functions, which are only available in certain
engines.

@@

% (\jsc{}=147, \veight{}=370, and \smonkey{}=110).
% (\jsc{}=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
To obtain test files included as attachments, we wrote a crawler to
visit the issue trackers of all engines listed in
Table~\ref{tab:engines} and we were able to retrieve a total of
\filesAttached{} files.  To mine tests from the textual descriptions we
proceeded as follows. First, we broke the text describing the issue in
paragraphs and used a binary classifier to label each paragraph as
``code'' or ``not code'' (\ie{}, natural language). Then, based on
that information, we merged consecutive paragraphs labeled as ``code''
and used a \js\ parser to check well-formedness of the retrieved code
fragment. Using that method we were able to retrieve a total of
\filesMining{} files. All those files were included in
Table~\ref{tab:test-suites}.

@@

\begin{table}
  %\vspace{-4ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  %\small
  \begin{tabular}{rr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & \percentSuiteTestJSC{}\\
    \veight{} & \percentSuiteTestVeight{} \\
    \chakra{} & \percentSuiteTestChakra{} \\
    \smonkey{} & \percentSuiteTestSM{} \\
    \hermes & xxx \\
    \bottomrule
  \end{tabular}
  %\normalsize
\end{table}

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc{}, \veight{}, and \smonkey\ whereas \chakra\ performs
worse compared to the other engines. Note also that \chakra\ is both
the engine that has the lowest passing ratio in this test suite and
the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. It is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:cross-testing}Number of failures with
    Test Transplantation.}
  \renewcommand*{\arraystretch}{0.9}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0
      JSC 2
      Spidermonkey 58
    }
    \jsc{} & - & 10 & 10 & 59   \\
    \veight{} & 41 & - & 3 & 5  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 281 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 282 & 146 & 39 & 369 \\
    \bottomrule
  \end{tabular}
  \vspace{-3ex}
\end{table}

@@

\sloppy The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} did not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture that by looking for error types like
\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
  we found cases where the test (or its harness) fails in an assertion
  because of an undefined property.}  \textbf{Other.} This category
includes other sources of false positives. For example, it includes
the cases where the test was valid for some previous version of the
spec but is no longer valid for the current spec.

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Severity'' shows the severity of confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test.  (We omitted the URLs of the issues to protect anonymity.)
Considering severity levels, we found that \jsc{}~\cite{jsc-severity}
and \smonkey{}~\cite{mozilla-severity} developers use five levels,
whereas \chakra{}~\cite{chakra-severity} and
\veight{}~\cite{v8-severity} developers use only three. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') in place of the severity level for the cases where
the bug report is pending confirmation. Of the
\noBugsTransplantation{} bugs we reported in this experiment,
\noBugsTransplantationConfirmed\ were promoted from the status ``New''
to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
not find any critical bugs, most of the bugs are seemingly important
as per the categorization given by engineers. Analyzing the issue
tracker of \chakra, we found that severity-1 bugs are indeed
rare. Considering the number of bug reports confirmed by developers,
\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
fixed). Considering the remaining engines, \veight{} developers
confirmed the \noTransVeightBugsReported{} bugs we reported, fixing
\noTransVeightBugsFixed{}. Curiously, Google
engineers confirmed the issued bug reports in a few hours. Overall, we
found that development teams of other engines, specially \jsc\, took
much longer to analyze bug reports as can be observed in the
\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}.
However, the bugs the \jsc{} team confirmed were quickly fixed.

@@

%% Note from the table that all bug reports still waiting for
%% confirmation are associated with the \jsc{} engine. A closer look at
%% the \jsc{} issue tracker showed that their triage process is slow
%% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
%%     bug tracker was defined as confirmed, however the bugs are
%%     included on a milestone for the next release following an internal
%%     priority.  }}

@@

\vspace{1ex}\noindent\textbf{Issue \#18,
  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
shows the test input we used to reveal a bug in \jsc{}. This test
originates from \jerry{} test suite; the bug was found during the test
transplantation experiment.

@@

According to the specification~\cite{ecmas262-array-sort}, the
parameter to the \CodeIn{Array.sort} function should be a comparable
object or an undefined value, otherwise it should throw a
\CodeIn{TypeError}. In this case, \jsc{} accepts a non-callable object
as argument to \CodeIn{sort} and the test fails in the subsequent
step. The other engines raise a \CodeIn{TypeError} as expected.

@@

This is a testcase original from the \jsc{} suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, but this test uses a long integer
instead. As result, the engine crashes. The team answered that this
was an incompatibility by design as the function was not expected to
receive such a long value.

>>>>

\begin{figure}[t]
%  \vspace{-2ex}
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}
  }
  \caption{\label{fig:summary}Summary of bug reports.\Gustavo{Não esquecer de atualizar as figuras.
  }}
  \vspace{-3ex}
\end{figure}

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google),
\smonkey{} (Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}).
Each stacked bar breaks down the bugs
per status (\eg{}, ``1-New''). The prefix number indicates the
ordering that status labels are assigned. Several of these
reports have the label ``3-Fixed'', indicating that bug fixes have
been incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{} and JavaScriptCore (\jsc).  We
reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed),
\noBugsBugsReportedHermes in \hermes,
and \noBugsBugsReportedSMonkey in \smonkey{}.
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation bugs (of which,
\noBugsTransplantationConfirmed were confirmed and
\noBugsTransplantationFixed were fixed) whereas differential testing
revealed \noBugsDifferentialTesting bugs (of which,
\noBugsDifferentialTestingConfirmed were confirmed and
\noBugsDifferentialTestingFixed were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Most bugs we found are of moderate severity.

@@

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is empirical:
we provide a comprehensive study analyzing the effectiveness of
test transplantation and differential testing
in revealing functional bugs in popular \javascript\ engines.
Additional contributions are:
1)~A number of bugs found and fixed.
We reported a total of \totalBugsReported bugs.
Of these, \totalBugsConfirmed bugs were confirmed and \totalBugsFixed bugs were fixed.
2)~An infrastructure for performing test transplantation and differential testing.
Both the scripts to run the experiments and the data processed are publicly available at \dataRepo.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:engines}Engines selected.}
  \begin{tabular}{cccrrr}
    \toprule
    Team & Name & URL & \# Stars  & DOB \\
    \midrule
    Apple & \jsc (WebKit) & \cite{jsc2018repo} & 3300+ & Jun 2001 \\
    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008 \\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009 \\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & 1100+ & Mar 1996 \\
    Facebook & \hermes & \cite{hermes2020repo} & 5400+ & Jul 2019 \\
   \bottomrule
  \end{tabular}
\end{table}

@@

Table~\ref{tab:test-suites} shows the breakdown of tests per
engine. Column ``full'' shows the number of test cases associated with
each engine. Column ``pass-in-par.''  shows the number of test cases
that pass in their parent engine. We discarded tests that fail in
their parent engine as we could not reliably indicate the reason for
the failure, so we assumed the test could be broken. We removed \testsThatFail{}
test cases that fail for that reason--\testsThatFailJSC{} tests from \jsc and
\testsThatFailSM{} tests from \smonkey. Column ``type-in-all''
shows the number of test cases whose executions do not throw
dynamic type errors in any of the engines because of an undefined variable or property.
These cases were captured by looking for the presence of \CodeIn{ReferenceError} and
\CodeIn{TypeError} in the output. A \CodeIn{ReferenceError}
(respectively, \CodeIn{TypeError}) is raised when test execution
attempts to access an undefined variable (respectively, property of an
object). We discarded those tests to avoid noise in the experiments as
they clearly indicate some missing feature as opposed to bugs. For
example, some tests use non-portable names (\eg{}, \jsc's
\CodeIn{drainMicrotasks()} and \smonkey{}'s \CodeIn{Error.lineNumber})
or use functions that, albeit part of the spec, not all engines
currently support. For the evaluation of test transplantation, we used
the \totalTestFilesForTestTransplantation{} tests included in the
dashed rectangle under column ``type-in-all'', \ie{}, all tests under
that column but the Test262 tests. We did not consider tests from the
conformance suite as they are more likely to indicate missing features
as opposed to bugs. In addition, engine developers have access to
these test and are encouraged to run them. Finally, column
``no-fail-in-all'' shows the tests for which all engines pass. Note
that the set of tests in this column is a subset of the
``type-in-all'' test set. This test set is used in the evaluation of
differential testing as fuzzing seeds. The guarantee that they pass in
all engines assures that, if discrepancies occur, they are related to
the changes in the input as opposed to the original cause of failure.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' (resp., ``no-fail-in-all'')
    shows the tests used for test transplantation (resp., cross-engine
    differential testing).\Gustavo{Terminar essa tabela}}  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{webkit} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v8} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    \chakra & \cite{chakracore}\\
    \hermes & \cite{hermes2020repo}\\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    Hermes & \cite{jsi} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{}\\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
depend on external libraries, which not all selected engines
support. We decided to discard those. For example, many tests we found
required a Node.js runtime~\cite{node} for execution. Also, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.
Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due. \lbrack{}Test Harness\rbrack{}~It is also
worth mentioning that some engines use a custom shell to run tests,
including a harness with specific assertions.  For that, we needed to
make minor changes in the testing infrastructure to be able to run the
tests uniformly across all engines. More precisely, we needed to mock
non-portable harness functions, which are only available in certain
engines.

@@

% (\jsc=147, \veight{}=370, and \smonkey{}=110).
% (\jsc=\Fix{XX}, \veight{}=\Fix{XX}, \smonkey{}=\Fix{XX})
To obtain test files included as attachments, we wrote a crawler to
visit the issue trackers of all engines listed in
Table~\ref{tab:engines} and we were able to retrieve a total of
\filesAttached{} files.  To mine tests from the textual descriptions we
proceeded as follows. First, we broke the text describing the issue in
paragraphs and used a binary classifier to label each paragraph as
``code'' or ``not code'' (\ie{}, natural language). Then, based on
that information, we merged consecutive paragraphs labeled as ``code''
and used a \js\ parser to check well-formedness of the retrieved code
fragment. Using that method we were able to retrieve a total of
\filesMining{} files. All those files were included in
Table~\ref{tab:test-suites}.

@@

\begin{table}
  %\vspace{-4ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  %\small
  \begin{tabular}{rr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc & \percentSuiteTestJSC{}\\
    \veight{} & \percentSuiteTestVeight{} \\
    \chakra{} & \percentSuiteTestChakra{} \\
    \smonkey{} & \percentSuiteTestSM{} \\
    \hermes & xxx \\
    \bottomrule
  \end{tabular}
  %\normalsize
\end{table}

Results show that there are still many unsupported scenarios as can be observed from the
percentages in the table. The number of passing tests is high and
similar for \jsc, \veight{}, and \smonkey\ whereas \chakra\ performs
worse compared to the other engines. Note also that \chakra\ is both
the engine that has the lowest passing ratio in this test suite and
the one we were able to find more bugs (as per
Figure~\ref{fig:summary}). Although it is plausible to find
correlation between the passing ratios and reliability as measured by
the number of bugs found, we do not imply causality. It is important
to note that failures in this conformance test suite indicates missing
features as opposed to bugs.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:cross-testing}Number of failures with
    Test Transplantation.}
  \renewcommand*{\arraystretch}{0.9}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0
      JSC 2
      Spidermonkey 58
    }
    \jsc & - & 10 & 10 & 59   \\
    \veight{} & 41 & - & 3 & 5  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 218 & 107 & - & 281 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 282 & 146 & 39 & 369 \\
    \bottomrule
  \end{tabular}
  \vspace{-3ex}
\end{table}

@@

\sloppy The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc defines a function with a tail-call
recursion. The test fails in all engines but \jsc, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} did not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture that by looking for error types like
\CodeIn{ReferenceError} and \CodeIn{TypeError}.\Comment{ For example,
  we found cases where the test (or its harness) fails in an assertion
  because of an undefined property.}  \textbf{Other.} This category
includes other sources of false positives. For example, it includes
the cases where the test was valid for some previous version of the
spec but is no longer valid for the current spec.

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Severity'' shows the severity of confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test.  (We omitted the URLs of the issues to protect anonymity.)
Considering severity levels, we found that \jsc~\cite{jsc-severity}
and \smonkey{}~\cite{mozilla-severity} developers use five levels,
whereas \chakra{}~\cite{chakra-severity} and
\veight{}~\cite{v8-severity} developers use only three. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') in place of the severity level for the cases where
the bug report is pending confirmation. Of the
\noBugsTransplantation{} bugs we reported in this experiment,
\noBugsTransplantationConfirmed\ were promoted from the status ``New''
to ``Confirmed''. Of these, \noBugsTransplantationSeverityTwo{} are severity-2 bugs.  Although we did
not find any critical bugs, most of the bugs are seemingly important
as per the categorization given by engineers. Analyzing the issue
tracker of \chakra, we found that severity-1 bugs are indeed
rare. Considering the number of bug reports confirmed by developers,
\chakra{} was the engine with the highest number--\bugsChakra{} (with \bugsChakraFixed{} bugs
fixed). Considering the remaining engines, \veight{} developers
confirmed the \noTransVeightBugsReported{} bugs we reported, fixing
\noTransVeightBugsFixed{}. Curiously, Google
engineers confirmed the issued bug reports in a few hours. Overall, we
found that development teams of other engines, specially \jsc\, took
much longer to analyze bug reports as can be observed in the
\jsc\ stacked bar from Figure~\ref{fig:stacked-engine}.
However, the bugs the \jsc team confirmed were quickly fixed.

@@

%% Note from the table that all bug reports still waiting for
%% confirmation are associated with the \jsc engine. A closer look at
%% the \jsc issue tracker showed that their triage process is slow
%% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
%%     bug tracker was defined as confirmed, however the bugs are
%%     included on a milestone for the next release following an internal
%%     priority.  }}

@@

\vspace{1ex}\noindent\textbf{Issue \#18,
  Table~\ref{tab:test-transplantation-bugs}.}  The code snippet below
shows the test input we used to reveal a bug in \jsc. This test
originates from \jerry{} test suite; the bug was found during the test
transplantation experiment.

@@

According to the specification~\cite{ecmas262-array-sort}, the
parameter to the \CodeIn{Array.sort} function should be a comparable
object or an undefined value, otherwise it should throw a
\CodeIn{TypeError}. In this case, \jsc accepts a non-callable object
as argument to \CodeIn{sort} and the test fails in the subsequent
step. The other engines raise a \CodeIn{TypeError} as expected.

@@

This is a testcase original from the \jsc suite that the
\radamsa\ fuzzer modified. The original test used the integer literal
3 as argument to \CodeIn{repeat()}, but this test uses a long integer
instead. As result, the engine crashes. The team answered that this
was an incompatibility by design as the function was not expected to
receive such a long value.
